Dominance Regions for Affine Cluster Algebras

### 2022-07-02 affine_dominance.tex
Slight modification for uniformity

  Given a sequence of signs $\beps=(\varepsilon_1,\varepsilon_2,\ldots,\varepsilon_r)$ with $\varepsilon_i\in\{\pm\}$, define a quiver $Q^{(r)}_\beps$ with vertices 
  \[\{(\ell,s)\in [n]\times\ZZ_{\ge0}:ns+\ell\le n+r\}\cup\{k:n+1\le k\le 2n\}\]
  and having the following arrows:
  \begin{itemize}
    \item an arrow $(\ell,s)\to (k,s)$ of weight $b_{k\ell}$ whenever $\ell<k$, $ns+\ell\le r$, and $\varepsilon_{ns+\ell}=+$;
    \item an arrow $(\ell,s)\to (k,s+1)$ of weight $-b_{k\ell}$ whenever $k<\ell$, $ns+\ell\le r$, and $\varepsilon_{ns+\ell}=+$;
    \item an arrow $(\ell,s)\to (\ell,s+1)$ of weight $-1$ whenever $ns+\ell\le r$;
    \item an arrow $(\ell,s)\to k$ of weight $\varepsilon_{ns+\ell}\bfc^{(ns+\ell)}_{k\ell}$ whenever $\varepsilon_{ns+\ell}=\sgn(\bfc^{(ns+\ell)}_{k\ell})$.
  \end{itemize}
  For $1\le\ell\le r$, write $\hat{\ell}$ for the vertex $(\ell,s)$ of $Q^{(r)}_\beps$ with $s$ maximal.
  For $n+1\le k\le 2n$, $\hat{k}=k$.
  Below we freely identify each vertex $(\ell,0)$ with $\ell$ itself.

  Given a sequence of signs $\beps=(\varepsilon_0,\varepsilon_{-1},\varepsilon_{-2},\ldots,\varepsilon_{-r+1})$ with $\varepsilon_i\in\{\pm\}$, define a quiver $Q^{(-r)}_\beps$ with vertices 
  \[\{(\ell,s)\in [n]\times\ZZ_{<0}:-n-r<ns+\ell\}\cup\{k:n+1\le k\le 2n\}\]
  and having the following arrows:
  \begin{itemize}
    \item an arrow $(\ell,s)\to (k,s)$ of weight $-b_{k\ell}$ whenever $k<\ell$, $-r<ns+\ell$, and $\varepsilon_{ns+\ell}=-$;
    \item an arrow $(\ell,s)\to (k,s-1)$ of weight $b_{k\ell}$ whenever $\ell<k$, $-r<ns+\ell$, and $\varepsilon_{ns+\ell}=-$;
    \item an arrow $(\ell,s)\to (\ell,s-1)$ of weight $-1$ whenever $-r<ns+\ell$.
    \item an arrow $(\ell,s)\to k$ of weight $\varepsilon_{ns+\ell}\bfc^{(ns+\ell)}_{k\ell}$ whenever $\varepsilon_{ns+\ell}=\sgn(\bfc^{(ns+\ell)}_{k\ell})$.
  \end{itemize}
  For $1\le\ell\le r$, write $\check{\ell}$ for the vertex $(\ell,s)$ of $Q^{(r)}_\beps$ with $s$ minimal.
  For $n+1\le k\le 2n$, $\check{k}=k$.
  Below we freely identify each vertex $(\ell,-1)$ with $\ell$ itself.

  Given a path $\fp\subset Q^{(\pm r)}_\beps$, write $\wt(\fp)$ for the product of the weights along the arrows in $\fp$.
  Let $i(\fp)$ and $t(\fp)$ denote the initial and terminal vertex along the path $\fp$.
  Below we only consider paths $\fp\subset Q^{(r)}_\beps$ with $i(\fp)=(\ell,0)$ for some $\ell$ and paths $\fp\subset Q^{(-r)}_\beps$ with $i(\fp)=(\ell,-1)$ for some $\ell$ or paths with $i(\fp)=k$ for some $n+1\le k\le 2n$.
  \begin{proposition}
    Consider $r>0$ with $r=ns+\ell$ for $1\le\ell\le n$.
    \begin{enumerate}
      \item For $\lambda\in\ZZ^n$, suppose the tropical transformation $\phi_{t_r}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_n,\lambda'_{n+1},\cdots,\lambda'_{2n})$ is given by
        \[
          E^{t_{r-1}}_{\ell,\varepsilon_r} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell+1}} E^{t_{ns-1}}_{n,\varepsilon_{ns}} \cdots E^{t_1}_{2,\varepsilon_2} E^{t_0}_{1,\varepsilon_1} \lambda
        \]
        with the signs $\beps=(\varepsilon_1,\cdots,\varepsilon_r)$ determined by $\lambda$.
        Then, for $1\le k\le 2n$, we have
        \[
          \lambda'_k=\sum\limits_{\fp\subset Q^{(r)}_\beps\!,\, t(\fp)=\hat{k}} \wt(\fp)\lambda_{i(\fp)}.
        \]
      \item For $\lambda\in\ZZ^n$, suppose the tropical transformation $\phi_{t_{-r}}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_n,\lambda'_{n+1},\cdots,\lambda'_{2n})$ is given by
        \[
          E^{t_{-r+1}}_{n-\ell+1,\varepsilon_{-r+1}} \cdots E^{t_{-r+\ell}}_{n,\varepsilon_{-r+\ell}} E^{t_{-ns+1}}_{1,\varepsilon_{-ns+1}} \cdots E^{t_{-1}}_{n-1,\varepsilon_{-1}} E^{t_0}_{n,\varepsilon_0} \lambda
        \]
        with the signs $\beps=(\varepsilon_0,\varepsilon_{-1},\cdots,\varepsilon_{-r+1})$ determined by $\lambda$.
        Then, for $1\le k\le 2n$, we have
        \[
          \lambda'_k=\sum\limits_{\fp\subset Q^{(-r)}_\beps\!,\, t(\fp)=\check{k}} \wt(\fp)\lambda_{i(\fp)}.
        \]
    \end{enumerate}
  \end{proposition}
  \begin{proof}
    We work by induction on $r$.
    Write $r=ns+\ell$.
    From Lemma~\ref{lem:transjective exchange matrices} and Lemma~\ref{lem:tropical signs}, we see that the $\ell$-th column of $\tilde B^{t_{r-1}}$ has the first $n$ entries non-negative and the last $n$ entries non-positive.

>>>>

  Given a sequence of signs $\beps=(\varepsilon_1,\varepsilon_2,\ldots,\varepsilon_r)$ with $\varepsilon_i\in\{\pm\}$, define a quiver $Q^{(r)}_\beps$ with vertices 
  \[\{(\ell,s)\in [n]\times\ZZ_{\ge0}:ns+\ell\le n+r\}\cup\{(n+k,0):1\le k\le n\}\]
  and having the following arrows:
  \begin{itemize}
    \item an arrow $(\ell,s)\to (k,s)$ of weight $b_{k\ell}$ whenever $\ell<k$, $ns+\ell\le r$, and $\varepsilon_{ns+\ell}=+$;
    \item an arrow $(\ell,s)\to (k,s+1)$ of weight $-b_{k\ell}$ whenever $k<\ell$, $ns+\ell\le r$, and $\varepsilon_{ns+\ell}=+$;
    \item an arrow $(\ell,s)\to (\ell,s+1)$ of weight $-1$ whenever $ns+\ell\le r$;
    \item an arrow $(\ell,s)\to (n+k,0)$ of weight $\varepsilon_{ns+\ell}\bfc^{(ns+\ell)}_{k\ell}$ whenever $\varepsilon_{ns+\ell}=\sgn(\bfc^{(ns+\ell)}_{k\ell})$.
  \end{itemize}
  For $1\le\ell\le r$, write $\hat{\ell}$ for the vertex $(\ell,s)$ of $Q^{(r)}_\beps$ with $s$ maximal.
  Below we freely identify each vertex $(\ell,0)$ with $\ell$ itself.

  Given a sequence of signs $\beps=(\varepsilon_0,\varepsilon_{-1},\varepsilon_{-2},\ldots,\varepsilon_{-r+1})$ with $\varepsilon_i\in\{\pm\}$, define a quiver $Q^{(-r)}_\beps$ with vertices 
  \[\{(\ell,s)\in [n]\times\ZZ_{<0}:-n-r<ns+\ell\}\cup\{(n+k,-1):1\le k\le n\}\]
  and having the following arrows:
  \begin{itemize}
    \item an arrow $(\ell,s)\to (k,s)$ of weight $-b_{k\ell}$ whenever $k<\ell$, $-r<ns+\ell$, and $\varepsilon_{ns+\ell}=-$;
    \item an arrow $(\ell,s)\to (k,s-1)$ of weight $b_{k\ell}$ whenever $\ell<k$, $-r<ns+\ell$, and $\varepsilon_{ns+\ell}=-$;
    \item an arrow $(\ell,s)\to (\ell,s-1)$ of weight $-1$ whenever $-r<ns+\ell$.
    \item an arrow $(\ell,s)\to (n+k,-1)$ of weight $\varepsilon_{ns+\ell}\bfc^{(ns+\ell)}_{k\ell}$ whenever $\varepsilon_{ns+\ell}=\sgn(\bfc^{(ns+\ell)}_{k\ell})$.
  \end{itemize}
  For $1\le\ell\le r$, write $\check{\ell}$ for the vertex $(\ell,s)$ of $Q^{(r)}_\beps$ with $s$ minimal.
  Below we freely identify each vertex $(\ell,-1)$ with $\ell$ itself.

  Given a path $\fp\subset Q^{(\pm r)}_\beps$, write $\wt(\fp)$ for the product of the weights along the arrows in $\fp$.
  Let $i(\fp)$ and $t(\fp)$ denote the initial and terminal vertex along the path $\fp$.
  Below we only consider paths $\fp\subset Q^{(r)}_\beps$ with $i(\fp)=(\ell,0)$ for some $\ell$ and paths $\fp\subset Q^{(-r)}_\beps$ with $i(\fp)=(\ell,-1)$ for some $\ell$.
  \begin{proposition}
    Consider $r>0$ with $r=ns+\ell$ for $1\le\ell\le n$.
    \begin{enumerate}
      \item For $\lambda\in\ZZ^n$, suppose the tropical transformation $\phi_{t_r}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_n,\lambda'_{n+1},\cdots,\lambda'_{2n})$ is given by
        \[
          E^{t_{r-1}}_{\ell,\varepsilon_r} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell+1}} E^{t_{ns-1}}_{n,\varepsilon_{ns}} \cdots E^{t_1}_{2,\varepsilon_2} E^{t_0}_{1,\varepsilon_1} \lambda
        \]
        with the signs $\beps=(\varepsilon_1,\cdots,\varepsilon_r)$ determined by $\lambda$.
        Then, for $1\le k\le 2n$, we have
        \[
          \lambda'_k=\sum\limits_{\fp\subset Q^{(r)}_\beps\!,\, t(\fp)=\hat{k}} \wt(\fp)\lambda_{i(\fp)}.
        \]
      \item For $\lambda\in\ZZ^n$, suppose the tropical transformation $\phi_{t_{-r}}(\tilde\lambda)=(\lambda'_1,\ldots,\lambda'_n,\lambda'_{n+1},\cdots,\lambda'_{2n})$ is given by
        \[
          E^{t_{-r+1}}_{n-\ell+1,\varepsilon_{-r+1}} \cdots E^{t_{-r+\ell}}_{n,\varepsilon_{-r+\ell}} E^{t_{-ns+1}}_{1,\varepsilon_{-ns+1}} \cdots E^{t_{-1}}_{n-1,\varepsilon_{-1}} E^{t_0}_{n,\varepsilon_0} \lambda
        \]
        with the signs $\beps=(\varepsilon_0,\varepsilon_{-1},\cdots,\varepsilon_{-r+1})$ determined by $\lambda$.
        Then, for $1\le k\le 2n$, we have
        \[
          \lambda'_k=\sum\limits_{\fp\subset Q^{(-r)}_\beps\!,\, t(\fp)=\check{k}} \wt(\fp)\lambda_{i(\fp)}.
        \]
    \end{enumerate}
  \end{proposition}
  \begin{proof}
    We work by induction on $r$.
    Write $r=ns+\ell$.
    From Lemma~\ref{lem:transjective exchange matrices} and Lemma~\ref{lem:tropical signs}, we see that the $\ell$-th column of $\tilde B^{t_{r-1}}$ has the first $n$ entries non-negative and the last $n$ entries non-positive.
